An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-10-24 latex_files/ch4/4-3-evaluation.tex
updated some images

\begin{Code}
------------------------------ python snippet ------------------------------  
  # Evaluation part
  res = romc.compute_divergence(wrapper, distance="Jensen-Shannon")                                 
  print("Jensen-Shannon divergence: %.3f" % res)
  # Jensen-Shannon divergence: 0.025

  nof_samples = len(romc.result.weights)
  ess = romc.compute_ess()
  print("Nof Samples: %d, ESS: %.3f" % (nof_samples, ess))
  # Nof Samples: 19300, ESS: 16138.825
----------------------------------------------------------------------------  
\end{Code}

>>>>

\begin{Code}
------------------------------ python snippet ------------------------------  
  # Evaluation part
  res = romc.compute_divergence(wrapper, distance="Jensen-Shannon")                                 
  print("Jensen-Shannon divergence: %.3f" % res)
  # Jensen-Shannon divergence: 0.035

  nof_samples = len(romc.result.weights)
  ess = romc.compute_ess()
  print("Nof Samples: %d, ESS: %.3f" % (nof_samples, ess))
  # Nof Samples: 19300, ESS: 16196.214
----------------------------------------------------------------------------  
\end{Code}

### 2021-10-24 latex_files/images/chapter3/example_marginal.tex
updated some images

\draw[draw=none,fill=color0] (axis cs:-2.57142857142857,0) rectangle (axis cs:-2.48571428571429,0.006208033765389);
\draw[draw=none,fill=color0] (axis cs:-2.48571428571429,0) rectangle (axis cs:-2.4,0.0261624280112821);
\draw[draw=none,fill=color0] (axis cs:-2.4,0) rectangle (axis cs:-2.31428571428571,0.0337007547263973);
\draw[draw=none,fill=color0] (axis cs:-2.31428571428571,0) rectangle (axis cs:-2.22857142857143,0.0363613406258499);
\draw[draw=none,fill=color0] (axis cs:-2.22857142857143,0) rectangle (axis cs:-2.14285714285714,0.0541896684870789);
\draw[draw=none,fill=color0] (axis cs:-2.14285714285714,0) rectangle (axis cs:-2.05714285714286,0.0670526704061584);
\draw[draw=none,fill=color0] (axis cs:-2.05714285714286,0) rectangle (axis cs:-1.97142857142857,0.0841007399119992);
\draw[draw=none,fill=color0] (axis cs:-1.97142857142857,0) rectangle (axis cs:-1.88571428571429,0.0882637860955287);
\draw[draw=none,fill=color0] (axis cs:-1.88571428571429,0) rectangle (axis cs:-1.8,0.107105098505383);
\draw[draw=none,fill=color0] (axis cs:-1.8,0) rectangle (axis cs:-1.71428571428571,0.134226458530087);
\draw[draw=none,fill=color0] (axis cs:-1.71428571428571,0) rectangle (axis cs:-1.62857142857143,0.13742807026801);
\draw[draw=none,fill=color0] (axis cs:-1.62857142857143,0) rectangle (axis cs:-1.54285714285714,0.172328991470496);
\draw[draw=none,fill=color0] (axis cs:-1.54285714285714,0) rectangle (axis cs:-1.45714285714286,0.159523545491678);
\draw[draw=none,fill=color0] (axis cs:-1.45714285714286,0) rectangle (axis cs:-1.37142857142857,0.181085502173434);
\draw[draw=none,fill=color0] (axis cs:-1.37142857142857,0) rectangle (axis cs:-1.28571428571429,0.198590015309879);
\draw[draw=none,fill=color0] (axis cs:-1.28571428571429,0) rectangle (axis cs:-1.2,0.221267556259859);
\draw[draw=none,fill=color0] (axis cs:-1.2,0) rectangle (axis cs:-1.11428571428571,0.234145572772051);
\draw[draw=none,fill=color0] (axis cs:-1.11428571428571,0) rectangle (axis cs:-1.02857142857143,0.277788991057236);
\draw[draw=none,fill=color0] (axis cs:-1.02857142857143,0) rectangle (axis cs:-0.942857142857143,0.250781241453748);
\draw[draw=none,fill=color0] (axis cs:-0.942857142857143,0) rectangle (axis cs:-0.857142857142857,0.265410460009239);
\draw[draw=none,fill=color0] (axis cs:-0.857142857142857,0) rectangle (axis cs:-0.771428571428571,0.303461442846629);
\draw[draw=none,fill=color0] (axis cs:-0.771428571428571,0) rectangle (axis cs:-0.685714285714285,0.302778779346469);
\draw[draw=none,fill=color0] (axis cs:-0.685714285714285,0) rectangle (axis cs:-0.6,0.294470204004708);
\draw[draw=none,fill=color0] (axis cs:-0.6,0) rectangle (axis cs:-0.514285714285714,0.32589124301026);
\draw[draw=none,fill=color0] (axis cs:-0.514285714285714,0) rectangle (axis cs:-0.428571428571428,0.307263137822596);
\draw[draw=none,fill=color0] (axis cs:-0.428571428571428,0) rectangle (axis cs:-0.342857142857143,0.310432718428548);
\draw[draw=none,fill=color0] (axis cs:-0.342857142857143,0) rectangle (axis cs:-0.257142857142857,0.313571769361836);
\draw[draw=none,fill=color0] (axis cs:-0.257142857142857,0) rectangle (axis cs:-0.171428571428571,0.322468416267153);
\draw[draw=none,fill=color0] (axis cs:-0.171428571428571,0) rectangle (axis cs:-0.0857142857142859,0.329442694767694);
\draw[draw=none,fill=color0] (axis cs:-0.0857142857142859,0) rectangle (axis cs:0,0.328704477273017);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.0857142857142859,0.315996626149429);
\draw[draw=none,fill=color0] (axis cs:0.0857142857142859,0) rectangle (axis cs:0.171428571428571,0.35869562652787);
\draw[draw=none,fill=color0] (axis cs:0.171428571428571,0) rectangle (axis cs:0.257142857142857,0.299321419039204);
\draw[draw=none,fill=color0] (axis cs:0.257142857142857,0) rectangle (axis cs:0.342857142857143,0.327344655623505);
\draw[draw=none,fill=color0] (axis cs:0.342857142857143,0) rectangle (axis cs:0.428571428571429,0.324602990921247);
\draw[draw=none,fill=color0] (axis cs:0.428571428571429,0) rectangle (axis cs:0.514285714285714,0.300242814569848);
\draw[draw=none,fill=color0] (axis cs:0.514285714285714,0) rectangle (axis cs:0.6,0.325196567835609);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.685714285714286,0.3008173729996);
\draw[draw=none,fill=color0] (axis cs:0.685714285714286,0) rectangle (axis cs:0.771428571428571,0.306931815801259);
\draw[draw=none,fill=color0] (axis cs:0.771428571428571,0) rectangle (axis cs:0.857142857142857,0.292671455749884);
\draw[draw=none,fill=color0] (axis cs:0.857142857142857,0) rectangle (axis cs:0.942857142857143,0.266064095296049);
\draw[draw=none,fill=color0] (axis cs:0.942857142857143,0) rectangle (axis cs:1.02857142857143,0.241445667943122);
\draw[draw=none,fill=color0] (axis cs:1.02857142857143,0) rectangle (axis cs:1.11428571428571,0.23182281521762);
\draw[draw=none,fill=color0] (axis cs:1.11428571428571,0) rectangle (axis cs:1.2,0.217147051423478);
\draw[draw=none,fill=color0] (axis cs:1.2,0) rectangle (axis cs:1.28571428571429,0.224310513797232);
\draw[draw=none,fill=color0] (axis cs:1.28571428571429,0) rectangle (axis cs:1.37142857142857,0.212377916164659);
\draw[draw=none,fill=color0] (axis cs:1.37142857142857,0) rectangle (axis cs:1.45714285714286,0.190746892354591);
\draw[draw=none,fill=color0] (axis cs:1.45714285714286,0) rectangle (axis cs:1.54285714285714,0.196218210084616);
\draw[draw=none,fill=color0] (axis cs:1.54285714285714,0) rectangle (axis cs:1.62857142857143,0.133681428800119);
\draw[draw=none,fill=color0] (axis cs:1.62857142857143,0) rectangle (axis cs:1.71428571428571,0.142913401618273);
\draw[draw=none,fill=color0] (axis cs:1.71428571428571,0) rectangle (axis cs:1.8,0.108955396863223);
\draw[draw=none,fill=color0] (axis cs:1.8,0) rectangle (axis cs:1.88571428571429,0.0924363415213623);
\draw[draw=none,fill=color0] (axis cs:1.88571428571429,0) rectangle (axis cs:1.97142857142857,0.0739859090188589);
\draw[draw=none,fill=color0] (axis cs:1.97142857142857,0) rectangle (axis cs:2.05714285714286,0.0907797314146689);
\draw[draw=none,fill=color0] (axis cs:2.05714285714286,0) rectangle (axis cs:2.14285714285714,0.0652904576612423);
\draw[draw=none,fill=color0] (axis cs:2.14285714285714,0) rectangle (axis cs:2.22857142857143,0.0433796619328517);
\draw[draw=none,fill=color0] (axis cs:2.22857142857143,0) rectangle (axis cs:2.31428571428571,0.0363613406258499);
\draw[draw=none,fill=color0] (axis cs:2.31428571428571,0) rectangle (axis cs:2.4,0.0359179096426075);
\draw[draw=none,fill=color0] (axis cs:2.4,0) rectangle (axis cs:2.48571428571429,0.0301533068604609);
\draw[draw=none,fill=color0] (axis cs:2.48571428571429,0) rectangle (axis cs:2.57142857142857,0.00665146474863107);

@@

-2.59322023391724 0
-2.49152541160583 0.0369433164596558
-2.38983058929443 0.0452905893325806
-2.28813552856445 0.0549525022506714
-2.18644070625305 0.0659897327423096
-2.08474564552307 0.0784285068511963
-1.98305082321167 0.0922528505325317
-1.88135588169098 0.107397437095642
-1.77966105937958 0.123741984367371
-1.67796611785889 0.141106963157654
-1.5762711763382 0.159253358840942
-1.27118647098541 0.21515953540802
-1.16949152946472 0.232988834381104
-1.06779658794403 0.249699831008911
-0.96610164642334 0.264856100082397
-0.864406824111938 0.278041839599609
-0.762711882591248 0.288881063461304
-0.661016941070557 0.297054767608643
-0.559322118759155 0.302316904067993
-0.457627058029175 0.304275751113892
-0.355932235717773 0.304529428482056
0.254237294197083 0.304565906524658
0.355932235717773 0.304529428482056
0.457627058029175 0.304275751113892
0.559322118759155 0.302316904067993
0.661016941070557 0.297054767608643
0.762711882591248 0.288881063461304
0.864406824111938 0.278041839599609
0.96610164642334 0.264856100082397
1.06779658794403 0.249699831008911
1.16949152946472 0.232988834381104
1.27118647098541 0.21515953540802
1.3728814125061 0.196650266647339
1.5762711763382 0.159253358840942
1.67796611785889 0.141106963157654
1.77966105937958 0.123741984367371
1.88135588169098 0.107397437095642
1.98305082321167 0.0922528505325317
2.08474564552307 0.0784285068511963
2.18644070625305 0.0659897327423096
2.28813552856445 0.0549525022506714
2.38983058929443 0.0452905893325806
2.49152541160583 0.0369433164596558
2.59322023391724 0

>>>>

\draw[draw=none,fill=color0] (axis cs:-2.57142857142857,0) rectangle (axis cs:-2.48571428571429,0.00620818024343236);
\draw[draw=none,fill=color0] (axis cs:-2.48571428571429,0) rectangle (axis cs:-2.4,0.0261630453116077);
\draw[draw=none,fill=color0] (axis cs:-2.4,0) rectangle (axis cs:-2.31428571428571,0.0337015498929184);
\draw[draw=none,fill=color0] (axis cs:-2.31428571428571,0) rectangle (axis cs:-2.22857142857143,0.0363621985686753);
\draw[draw=none,fill=color0] (axis cs:-2.22857142857143,0) rectangle (axis cs:-2.14285714285714,0.054190947087826);
\draw[draw=none,fill=color0] (axis cs:-2.14285714285714,0) rectangle (axis cs:-2.05714285714286,0.0670542525083721);
\draw[draw=none,fill=color0] (axis cs:-2.05714285714286,0) rectangle (axis cs:-1.97142857142857,0.0841027242620032);
\draw[draw=none,fill=color0] (axis cs:-1.97142857142857,0) rectangle (axis cs:-1.88571428571429,0.0882658686722632);
\draw[draw=none,fill=color0] (axis cs:-1.88571428571429,0) rectangle (axis cs:-1.8,0.107107625641326);
\draw[draw=none,fill=color0] (axis cs:-1.8,0) rectangle (axis cs:-1.71428571428571,0.134229125094031);
\draw[draw=none,fill=color0] (axis cs:-1.71428571428571,0) rectangle (axis cs:-1.62857142857143,0.137431312871964);
\draw[draw=none,fill=color0] (axis cs:-1.62857142857143,0) rectangle (axis cs:-1.54285714285714,0.172331556064062);
\draw[draw=none,fill=color0] (axis cs:-1.54285714285714,0) rectangle (axis cs:-1.45714285714286,0.159526808938298);
\draw[draw=none,fill=color0] (axis cs:-1.45714285714286,0) rectangle (axis cs:-1.37142857142857,0.181088273376146);
\draw[draw=none,fill=color0] (axis cs:-1.37142857142857,0) rectangle (axis cs:-1.28571428571429,0.198593700028377);
\draw[draw=none,fill=color0] (axis cs:-1.28571428571429,0) rectangle (axis cs:-1.2,0.221271776053061);
\draw[draw=none,fill=color0] (axis cs:-1.2,0) rectangle (axis cs:-1.11428571428571,0.234818762077649);
\draw[draw=none,fill=color0] (axis cs:-1.11428571428571,0) rectangle (axis cs:-1.02857142857143,0.276972225850834);
\draw[draw=none,fill=color0] (axis cs:-1.02857142857143,0) rectangle (axis cs:-0.942857142857143,0.250286660370399);
\draw[draw=none,fill=color0] (axis cs:-0.942857142857143,0) rectangle (axis cs:-0.857142857142857,0.266079382024805);
\draw[draw=none,fill=color0] (axis cs:-0.857142857142857,0) rectangle (axis cs:-0.771428571428571,0.303023660053582);
\draw[draw=none,fill=color0] (axis cs:-0.771428571428571,0) rectangle (axis cs:-0.685714285714285,0.303811444292793);
\draw[draw=none,fill=color0] (axis cs:-0.685714285714285,0) rectangle (axis cs:-0.6,0.294340015485417);
\draw[draw=none,fill=color0] (axis cs:-0.6,0) rectangle (axis cs:-0.514285714285714,0.325167704449779);
\draw[draw=none,fill=color0] (axis cs:-0.514285714285714,0) rectangle (axis cs:-0.428571428571428,0.30751913529919);
\draw[draw=none,fill=color0] (axis cs:-0.428571428571428,0) rectangle (axis cs:-0.342857142857143,0.309628234907852);
\draw[draw=none,fill=color0] (axis cs:-0.342857142857143,0) rectangle (axis cs:-0.257142857142857,0.314430015080012);
\draw[draw=none,fill=color0] (axis cs:-0.257142857142857,0) rectangle (axis cs:-0.171428571428571,0.322025576461367);
\draw[draw=none,fill=color0] (axis cs:-0.171428571428571,0) rectangle (axis cs:-0.0857142857142859,0.330218732748452);
\draw[draw=none,fill=color0] (axis cs:-0.0857142857142859,0) rectangle (axis cs:0,0.327214742275935);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.0857142857142859,0.316669244232633);
\draw[draw=none,fill=color0] (axis cs:0.0857142857142859,0) rectangle (axis cs:0.171428571428571,0.358477864714324);
\draw[draw=none,fill=color0] (axis cs:0.171428571428571,0) rectangle (axis cs:0.257142857142857,0.300973118739705);
\draw[draw=none,fill=color0] (axis cs:0.257142857142857,0) rectangle (axis cs:0.342857142857143,0.326183215390922);
\draw[draw=none,fill=color0] (axis cs:0.342857142857143,0) rectangle (axis cs:0.428571428571429,0.324785323789832);
\draw[draw=none,fill=color0] (axis cs:0.428571428571429,0) rectangle (axis cs:0.514285714285714,0.300400548746278);
\draw[draw=none,fill=color0] (axis cs:0.514285714285714,0) rectangle (axis cs:0.6,0.324864903010947);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.685714285714286,0.301298442599607);
\draw[draw=none,fill=color0] (axis cs:0.685714285714286,0) rectangle (axis cs:0.771428571428571,0.30662874891955);
\draw[draw=none,fill=color0] (axis cs:0.771428571428571,0) rectangle (axis cs:0.857142857142857,0.292636319456018);
\draw[draw=none,fill=color0] (axis cs:0.857142857142857,0) rectangle (axis cs:0.942857142857143,0.267089387485241);
\draw[draw=none,fill=color0] (axis cs:0.942857142857143,0) rectangle (axis cs:1.02857142857143,0.240312230825788);
\draw[draw=none,fill=color0] (axis cs:1.02857142857143,0) rectangle (axis cs:1.11428571428571,0.231829286054268);
\draw[draw=none,fill=color0] (axis cs:1.11428571428571,0) rectangle (axis cs:1.2,0.217155177979677);
\draw[draw=none,fill=color0] (axis cs:1.2,0) rectangle (axis cs:1.28571428571429,0.224316807381749);
\draw[draw=none,fill=color0] (axis cs:1.28571428571429,0) rectangle (axis cs:1.37142857142857,0.212381425709292);
\draw[draw=none,fill=color0] (axis cs:1.37142857142857,0) rectangle (axis cs:1.45714285714286,0.190750892513498);
\draw[draw=none,fill=color0] (axis cs:1.45714285714286,0) rectangle (axis cs:1.54285714285714,0.196222839837058);
\draw[draw=none,fill=color0] (axis cs:1.54285714285714,0) rectangle (axis cs:1.62857142857143,0.133683582005886);
\draw[draw=none,fill=color0] (axis cs:1.62857142857143,0) rectangle (axis cs:1.71428571428571,0.142916773648167);
\draw[draw=none,fill=color0] (axis cs:1.71428571428571,0) rectangle (axis cs:1.8,0.108957967656803);
\draw[draw=none,fill=color0] (axis cs:1.8,0) rectangle (axis cs:1.88571428571429,0.0924385225491971);
\draw[draw=none,fill=color0] (axis cs:1.88571428571429,0) rectangle (axis cs:1.97142857142857,0.0739876547102644);
\draw[draw=none,fill=color0] (axis cs:1.97142857142857,0) rectangle (axis cs:2.05714285714286,0.0907818733549252);
\draw[draw=none,fill=color0] (axis cs:2.05714285714286,0) rectangle (axis cs:2.14285714285714,0.065291998184192);
\draw[draw=none,fill=color0] (axis cs:2.14285714285714,0) rectangle (axis cs:2.22857142857143,0.043380685472388);
\draw[draw=none,fill=color0] (axis cs:2.22857142857143,0) rectangle (axis cs:2.31428571428571,0.0363621985686753);
\draw[draw=none,fill=color0] (axis cs:2.31428571428571,0) rectangle (axis cs:2.4,0.0359187571227155);
\draw[draw=none,fill=color0] (axis cs:2.4,0) rectangle (axis cs:2.48571428571429,0.0301540183252429);
\draw[draw=none,fill=color0] (axis cs:2.48571428571429,0) rectangle (axis cs:2.57142857142857,0.00665162168939181);

@@

-2.89830508474576 0
-2.79661016949153 0
-2.69491525423729 0
-2.59322033898305 0
-2.49152542372881 0.036943365219351
-2.38983050847458 0.0452905809004646
-2.28813559322034 0.0549525585640254
-2.1864406779661 0.0659897576831711
-2.08474576271186 0.0784284692399008
-1.98305084745763 0.0922527949339697
-1.88135593220339 0.107397436643172
-1.77966101694915 0.123741930739631
-1.67796610169492 0.141106964487117
-1.57627118644068 0.159253358442953
-1.47457627118644 0.177884185408375
-1.3728813559322 0.19665032476711
-1.27118644067797 0.215159529401958
-1.16949152542373 0.232988825745372
-1.06779661016949 0.24969979654604
-0.966101694915254 0.264856035195966
-0.864406779661017 0.278041836013959
-0.762711864406779 0.288881021349384
-0.661016949152542 0.297054723966203
-0.559322033898305 0.30231695501038
-0.457627118644067 0.304275803005703
-0.35593220338983 0.304529357038898
-0.254237288135593 0.304565924185496
-0.152542372881356 0.304568537614607
-0.0508474576271185 0.304568582253443
0.050847457627119 0.304568582253443
0.152542372881356 0.304568537614607
0.254237288135593 0.304565924185496
0.355932203389831 0.304529357038898
0.457627118644068 0.304275803005703
0.559322033898305 0.30231695501038
0.661016949152542 0.297054723966203
0.76271186440678 0.288881021349384
0.864406779661017 0.278041836013959
0.966101694915254 0.264856035195966
1.06779661016949 0.24969979654604
1.16949152542373 0.232988825745372
1.27118644067797 0.215159529401958
1.3728813559322 0.19665032476711
1.47457627118644 0.177884185408375
1.57627118644068 0.159253358442953
1.67796610169492 0.141106964487117
1.77966101694915 0.123741930739631
1.88135593220339 0.107397436643172
1.98305084745763 0.0922527949339697
2.08474576271187 0.0784284692399007
2.1864406779661 0.065989757683171
2.28813559322034 0.0549525585640254
2.38983050847458 0.0452905809004645
2.49152542372881 0.0369433652193509
2.59322033898305 0
2.69491525423729 0
2.79661016949153 0
2.89830508474576 0
